---
title: " Data Visualization I Data Practical 5"
author: "Raphaël Krieg"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: 
  github_document:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message= F , warning= F}
library(readr)
library(dslabs)
library(tidyverse)
library(knitr)
library(ggplot2)
```

## Dataset description and modification wide into long.

I chose the `divorce_margarine` dataset. We have the *divorce rate in the state of Maine* in the U.S and the *consumption of margarine per capita*. Both are **numeric** and **continuous**. The last variable is the *year*, a **quantitative discrete** variable.
```{r}
str(divorce_margarine)
names(divorce_margarine)[1] <-'Divorce'
names(divorce_margarine)[2] <-'Margarine'
names(divorce_margarine)[3] <-'Year'
df_wide <- data.frame(divorce_margarine)
df_wide %>% kable()
```



```{r}
str(divorce_margarine)
names(divorce_margarine)[1] <-'Divorce'
names(divorce_margarine)[2] <-'Margarine'
names(divorce_margarine)[3] <-'Year'
data_long <- gather(divorce_margarine, condition, measurement, Divorce:Year, factor_key=TRUE)
data_long %>% kable()
```

## Data visualization via ggplot.

```{r}
ggplot(divorce_margarine, aes(Divorce, Margarine)) + 
  geom_line (colour = "grey50") + 
  geom_point(aes(colour = Margarine))
```

## Uniting

```{r}
united_marga_divo <- divorce_margarine %>% unite(unified)
head(united_marga_divo) %>% kable()
```


## Separating

```{r}
separate_marga_divo <- united_marga_divo %>% separate(unified, into=c("Divorce","Margarine", "year"), sep="_")
head(separate_marga_divo) %>% kable()
```

# References

divorce_margarine function—RDocumentation. (n.d.). Retrieved June 20, 2022, from https://www.rdocumentation.org/packages/dslabs/versions/0.7.4/topics/divorce_margarine
