---
title: "Data Modeling Data Practical 7"
author: "Raphaël Krieg"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: 
  github_document:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message= F , warning= F}
library(readr)
library(dslabs)
library(tidyverse)
library(knitr)
library(ggplot2)
```

# I'm a Star Wars fan !
### Description of the dataset

This dataset is composed of several variables. See below for more information about them (I' won't describe them all :)
```{r}
starwars1 <- na.omit(starwars)
starwars1
```



```{r}
ggplot(starwars1, aes(y=eye_color))+
  geom_bar(aes(fill=homeworld))+  
  theme(axis.text.y = element_text(angle = 360, vjust = 0.3, hjust=1,size=6))
```
## Hypothesis formulation 

H1: Planet origin has an impact on the color of your eyes.
Ho: Color of eyes is not influenced by the planet origin.

## Statistical test

```{r}
chisq.test(table(starwars1$homeworld,starwars1$eye_color))
```
We cannot reject HO meaning that the homeworld seem to dictate which color will be your eyes.

# References

Starwars characters—Starwars. (n.d.). Retrieved June 21, 2022, from https://dplyr.tidyverse.org/reference/starwars.html
