---
title: "Data Wrangling Data Practical 4 "
author: "Raphaël Krieg"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: 
  github_document:
    toc: true
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r message=FALSE, warning=FALSE}
library(knitr)
library(dplyr)
library(readr)
library(dslabs)
```

## Filtering 
Let's `filter()` the data for the Japan and put them in a dataframe.
```{r}
Japan_country_filter <- gapminder %>% 
  filter(country == "Japan")
```

Now let's do the same for the Brazil.
```{r}
Brazil_country_filter <- gapminder %>% 
  filter(country == "Brazil")
```

## Selecting
Now `select()` some interesting variable inside our new DF.
```{r}
Japan_selected <- Japan_country_filter %>%
  select(fertility, population, year)
  
str(Japan_selected)
head(Japan_selected) %>% kable()
tail(Japan_selected) %>% kable()
```

Same for Brazil.
```{r}
Brazil_selected <- Brazil_country_filter %>%
  select(fertility, population, year)
  
str(Brazil_selected)
head(Brazil_selected) %>% kable()
tail(Brazil_selected) %>% kable()
```

## Arranging 

```{r}
Japan_selected %>%
  arrange(year)
```
We can see above that the fertility rate drops along the years. However the population seems to increase. Suggesting that the increase of popluation has inertia. If the Fertility rate continues to drop, the popluation should also decrease. 

```{r}
Brazil_selected %>%
  arrange(year)
```

The fertility rate in 1960 was significantly higher in Brazil than in Japan. We see similar pattern as decribed above. People have less children as the population increases. Better health care and high life expectancy could also explain why the population is increase as the fertility rate is decreasing. People need "less" children to unsure a future.

## Group by and Summarise

```{r}
na.omit(gapminder) %>%
  group_by(country) %>%
  summarize(total_fertility = sum (fertility))
```


```{r}
na.omit(gapminder) %>%
  group_by(country) %>%
  summarize(total_fertility = sum (fertility)) %>%
  arrange(desc(total_fertility)) %>%
  head()
```
```{r}
na.omit(gapminder) %>%
  group_by(country) %>%
  summarize(total_fertility = sum (fertility)) %>%
  arrange(desc(total_fertility)) %>%
  tail()
```
We can see that the Rwanda is the most fertile country across the years and that Ireland is the least one. 

## Merging

Let's 'merge' the `results_us_election_2016` and `murders` datasets. 
```{r}
head(full_join(results_us_election_2016, murders)) %>% kable()
```
We could `arrange` the data by the number of murders in realtionship with the number of votes for a particular candidate. Ratio with the population would inform us if there is more murder in region voting for a particular candidate. 

# References

Jennifer Bryan (NA). gapminder: Data from Gapminder.
https://github.com/jennybc/gapminder,
http://www.gapminder.org/data/,
https://doi.org/10.5281/

Rogers, S. (2011, October 5). The murder map of London’s boroughs. The Guardian. http://www.theguardian.com/news/datablog/interactive/2011/oct/05/murder-london-map


WIlliams, Jack, 2022, "Elections Performance Index 2016", https://doi.org/10.7910/DVN/TSUQOA, Harvard Dataverse, V2, UNF:6:p1RbweyWRBJUm7A957ZaAQ== [fileUNF]

