---
title: "Data Data Practical 3"
author: "Raphaël Krieg"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: 
  github_document:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r message=FALSE, warning=FALSE}
library(knitr)
library(dplyr)
library(readr)
library(dslabs)
```


### Dataset 1 - Built-in R dataset

In the following code-chunk, I load the built-in R dataset called "trees"

```{r}
data(trees)
str(trees)
```


We can see that there are 3 **numerical** variables: 
1. [Girth](https://en.wikipedia.org/wiki/Tree_girth_measurement) 
2. [Heigth](https://en.wikipedia.org/wiki/Tree_height_measurement) 
3. [Volume](https://en.wikipedia.org/wiki/Tree_volume_measurement)

These three variables are **quantitve and continuous**


### Dataset 2 - The Pudding Dataset

Here we have a fun exemple of the `mars_weather` dataset. For more information about the different variables please follow this [link](https://data.world/the-pudding/mars-weather)

```{r}
mars_weather <- read.csv("https://raw.githubusercontent.com/the-pudding/data/master/mars-weather/mars-weather.csv")
str(mars_weather)
```

This dataset includes **10 variables**

1. *id* Type: Number. **Quantitative and disrcete**
2. *terrestrial_date* Type: Date. **Qualitative and ordinal**
3. *sol* Type: Number. **Quantitative and discrete**
4. *Ls* Type: Number. **Quantitative and discrete**
5. *month* Type: Text. **Qualitative and ordinal**
6. *min_temp* Type: Number. **Quantitative and continuous**
7. *max_temp* Type: Number. **Quantitative and continuous**
8. *pressure* Type: Number. **Quantitative and continuous**
9. *wind_speed* Type: Number. **Quantitative and continuous**
10. *atmo_opacity* Type: Text. **Qualitative and nominal**


### Dataset 3 - The Dplyr Dataset

The next dataset is recovered from the extended built-in Datasets from R via the dplyr package.

[Information](https://search.r-project.org/CRAN/refmans/FlexDir/html/oliveoil.html) about the dataset `olive`.

```{r}
str(olive)
```

This dataset has **10 variables**

1. *region* Type: Factor **Qualitative and discrete**
2. *area* Type: Factor.**Qualitative and discrete**
3. to 10. Are chemicals values. **Quantitatives and continuous**

# References

Atkinson, A. C. (1985) Plots, Transformations and Regression. Oxford University Press.

Azzalini, A., Menardi, G. (2014). Clustering via Nonparametric Density Estimation: The R Package pdfCluster. Journal of Statistical Software, 57(11), 1-26, URL http://www.jstatsoft.org/v57/i11/.

Azzalini A., Torelli N. (2007). Clustering via nonparametric density estimation. Statistics and
Computing, 17, 71-80.

Data sets. (2022). [HTML]. The Pudding. https://github.com/the-pudding/data/blob/44a0a67f932489ed5ae0552b04bd9f82b97125dd/mars-weather/mars-weather.csv (Original work published 2017)
